

```{r setup, include=FALSE}

# This chunk shows/hides the code in your final report. When echo = TRUE, the code
# is shown in the report. When echo = FALSE, the code is hidden from the final report.
# We would like to see your code, so please leave the setting as is during the course.
# This chunk will not show up in your reports, so you can safely ignore its existence.

knitr::opts_chunk$set(echo = TRUE)

```



```{r}
#setwd("C:/") #Don't forget to set your working directory before you start!
library("tidyverse")
library("tidymodels")
library("plotly")
library("skimr")
library("dplyr")
library("lubridate")
library("caret")
library("car")
library("e1071")
library("xgboost")
#library("gg")
```

```{r}
airdffTrain <- read_csv('airbnbTrain.csv')
airdffTest <- read_csv('airbnbTest.csv')
```

```{r}
#str(airdffTrain)
```



```{r}
#Clearning
airdffTrain$cleaning_fee <- (gsub("\\$", "", airdffTrain$cleaning_fee))
airdffTrain$cleaning_fee <- as.numeric(gsub("\\,", "", airdffTrain$cleaning_fee))
airdffTrain$extra_people <- (gsub("\\$", "", airdffTrain$extra_people))
airdffTrain$extra_people <- as.numeric(gsub("\\,", "", airdffTrain$extra_people))
airdffTrain$host_response_rate <- as.numeric(gsub("\\%", "", airdffTrain$host_response_rate))
airdffTrain$price <- (gsub("\\$", "", airdffTrain$price))
airdffTrain$price <- as.double(gsub("\\,", "", airdffTrain$price))
airdffTrain$security_deposit <- (gsub("\\$", "", airdffTrain$security_deposit))
airdffTrain$security_deposit <- as.numeric(gsub("\\,", "", airdffTrain$security_deposit))
airdffTrain$weekly_price <- (gsub("\\$", "", airdffTrain$weekly_price))
airdffTrain$weekly_price <- as.numeric(gsub("\\,", "", airdffTrain$weekly_price))

str(airdffTrain)
```

```{r}
#Cleaning - 2
airdffTest$cleaning_fee <- (gsub("\\$", "", airdffTest$cleaning_fee))
airdffTest$cleaning_fee <- as.numeric(gsub("\\,", "", airdffTest$cleaning_fee))
airdffTest$extra_people <- (gsub("\\$", "", airdffTest$extra_people))
airdffTest$extra_people <- as.numeric(gsub("\\,", "", airdffTest$extra_people))
airdffTest$host_response_rate <- as.numeric(gsub("\\%", "", airdffTest$host_response_rate))
airdffTest$price <- (gsub("\\$", "", airdffTest$price))
airdffTest$price <- as.double(gsub("\\,", "", airdffTest$price))
airdffTest$security_deposit <- (gsub("\\$", "", airdffTest$security_deposit))
airdffTest$security_deposit <- as.numeric(gsub("\\,", "", airdffTest$security_deposit))
airdffTest$weekly_price <- (gsub("\\$", "", airdffTest$weekly_price))
airdffTest$weekly_price <- as.numeric(gsub("\\,", "", airdffTest$weekly_price))
```

```{r}
#cleaning 3
airdffTrain$price <- ifelse(is.na(airdffTrain$price), mean(airdffTrain$price, na.rm=TRUE), airdffTrain$price)
airdffTest$price <- ifelse(is.na(airdffTest$price), mean(airdffTest$price, na.rm=TRUE), airdffTest$price)
#airdffTrain$cleaning_price <- ifelse(is.na(airdffTrain$cleaning_price), mean(airdffTrain$cleaning_price, na.rm=TRUE), airdffTrain$cleaning_price)
#airdffTest$cleaning_price <- ifelse(is.na(airdffTest$cleaning_price), mean(airdffTest$cleaning_price, na.rm=TRUE), airdffTest$cleaning_price)
airdffTrain$host_response_rate <- ifelse(is.na(airdffTrain$host_response_rate), mean(airdffTrain$host_response_rate, na.rm=TRUE), airdffTrain$host_response_rate)
airdffTest$host_response_rate <- ifelse(is.na(airdffTest$host_response_rate), mean(airdffTest$host_response_rate, na.rm=TRUE), airdffTest$host_response_rate)
airdffTrain$availability_365 <- ifelse(is.na(airdffTrain$availability_365), mean(airdffTrain$availibility_365, na.rm=TRUE), airdffTrain$availability_365)
airdffTest$availability_365 <- ifelse(is.na(airdffTest$availability_365), mean(airdffTest$availability_365, na.rm=TRUE), airdffTest$availability_365)
airdffTest$security_deposit <- ifelse(is.na(airdffTest$security_deposit), mean(airdffTest$security_deposit, na.rm=TRUE), airdffTest$security_deposit)
airdffTrain$security_deposit <- ifelse(is.na(airdffTrain$security_deposit), mean(airdffTrain$security_deposit, na.rm=TRUE), airdffTrain$security_deposit)
airdffTest$bedrooms <- ifelse(is.na(airdffTest$bedrooms), mean(airdffTest$bedrooms, na.rm=TRUE), airdffTest$bedrooms)
airdffTrain$bedrooms <- ifelse(is.na(airdffTrain$bedrooms), mean(airdffTrain$bedrooms, na.rm=TRUE), airdffTrain$bedrooms)
airdffTrain$bathrooms <- ifelse(is.na(airdffTrain$bathrooms), mean(airdffTrain$bathrooms, na.rm=TRUE), airdffTrain$bathrooms)
airdffTest$bathrooms <- ifelse(is.na(airdffTest$bathrooms), mean(airdffTest$bathrooms, na.rm=TRUE), airdffTest$bathrooms)
airdffTest$review_scores_rating <- ifelse(is.na(airdffTest$review_scores_rating), mean(airdffTest$review_scores_rating, na.rm=TRUE), airdffTest$review_scores_rating)
airdffTrain$review_scores_rating <- ifelse(is.na(airdffTrain$review_scores_rating), mean(airdffTrain$review_scores_rating, na.rm=TRUE), airdffTrain$review_scores_rating)
airdffTrain$beds <- ifelse(is.na(airdffTrain$beds), mean(airdffTrain$beds, na.rm=TRUE), airdffTrain$beds)
airdffTest$beds <- ifelse(is.na(airdffTest$beds), mean(airdffTest$beds, na.rm=TRUE), airdffTest$beds)
```

#XG Boost for overall US Data 

```{r}
trainx <- select(airdffTrain,-c('high_booking_rate'))
```

```{r}
dttrain = data.matrix(trainx)
dttest = data.matrix(airdffTest)
```

```{r}
dtrain <- xgb.DMatrix(data = dttrain, label = airdffTrain$high_booking_rate)
```

```{r}
bstair<- xgboost(data=dtrain, max.depth = 14, eta =0.0390,min_child_weight = 2,nthread =8,nrounds = 1200, max_delta_step = 2,colsample_bytree = 0.44, objective = "binary:logistic", verbose = FALSE)
```


```{r}
pred <- predict(bstair, dttest)
x <- data.frame(pred)
```

```{r}
airdffTrain$id
```


```{r}
#Excel extraction
#my_solution <- data.frame(id = airdffTests$id, high_booking_rate = pred)
```

```{r}
set.seed(123)
train <- airdffTrain %>%sample_frac(0.7)
test <- dplyr::setdiff(airdffTrain,train)
```

```{r}
trainx <- select(train,-c('high_booking_rate'))
testx <- select(test,-c('high_booking_rate'))
```

```{r}
dttrain = data.matrix(trainx)
dttest = data.matrix(testx)
```

```{r}
dtrain <- xgb.DMatrix(data = dttrain, label = train$high_booking_rate)
dtest <- xgb.DMatrix(data = dttest, label = test$high_booking_rate)
```

```{r}
bstair<- xgboost(data=dtrain, max.depth = 14, eta =0.0390,min_child_weight = 2,nthread =8,nrounds = 1200, max_delta_step = 2,colsample_bytree = 0.44, objective = "binary:logistic",verbose = FALSE)
```

```{r}
pred <- predict(bstair, dttest)
pred
```

```{r}
library (ROCR);

y <- test$high_booking_rate
predictions <- pred

predx <- prediction(predictions, y);

# Recall-Precision curve             
RP.perf <- performance(predx, "prec", "rec");

plot (RP.perf);

# ROC curve
ROC.perf <- performance(predx, "tpr", "fpr");
plot (ROC.perf);

# ROC area under the curve
auc.tmp <- performance(predx,"auc");
auc <- as.numeric(auc.tmp@y.values)

auc
```


```{r}
class_performance <- function(confusion_matrix){
  
  TP <- confusion_matrix[2,2]
  TN <- confusion_matrix[1,1]
  FP <- confusion_matrix[1,2]
  FN <- confusion_matrix[2,1]
  acc <- (TP+TN)/(TP+TN+FP+FN)
  tpr <- TP/(TP+FN)
  tnr <- TN/(TN+FP)
  return(c(acc,tpr,tnr))
}
#Confusion matrix function
confusion_matrix <- function(pred, actuals, cutoff){
  
  classifications <- ifelse(pred>cutoff,1,0)
  
  
  confusion_matrix <- table(actuals,classifications)
}

cm1=confusion_matrix(pred,test$high_booking_rate,0.6)
cm1
metrics1=class_performance(cm1)
metrics1
```


#XG Boost for Hawaii and analysis

```{r}
airdffTrainHawaii <- airdffTrain%>% filter(state == "HI") #18 rows missing
airdffTestHawaii <- airdffTest%>% filter(state == "HI")
```

```{r}
airdffTrainHawaii[airdffTrainHawaii$id==1044384, "market"] <- "Maui"
airdffTrainHawaii[airdffTrainHawaii$id==1197255, "market"] <- "The Big Island"
airdffTrainHawaii[airdffTrainHawaii$id==1074239, "market"] <- "Oahu"
airdffTrainHawaii[airdffTrainHawaii$id==1069364, "market"] <- "The Big Island"
airdffTrainHawaii[airdffTrainHawaii$id==1046942, "market"] <- "Maui"
airdffTrainHawaii[airdffTrainHawaii$id==1138892, "market"] <- "Kauai"
airdffTrainHawaii[airdffTrainHawaii$id==1061324, "market"] <- "Oahu"
airdffTrainHawaii[airdffTrainHawaii$id==1174621, "market"] <- "The Big Island"
airdffTrainHawaii[airdffTrainHawaii$id==1086618, "market"] <- "The Big Island"
airdffTrainHawaii[airdffTrainHawaii$id==1128414, "market"] <- "The Big Island"
airdffTrainHawaii[airdffTrainHawaii$id==1143164, "market"] <- "Maui"
airdffTrainHawaii[airdffTrainHawaii$market=="Big Island", "market"] <- "The Big Island"
airdffTrainHawaii[airdffTrainHawaii$market=="Other (International)", "market"] <- "Other (Domestic)"
```

```{r}
#median number of bedrooms
airdffTrainHawaii%>%
  group_by(high_booking_rate)%>%
  summarise(median(bedrooms))
```

```{r}
#Mean number of bedrooms in high booking rate locations
airdffTrainHawaii%>%
  group_by(high_booking_rate)%>%
  summarise(mean(bedrooms))
```

```{r}
#Bathrooms
airdffTrainHawaii%>%
   group_by(high_booking_rate)%>%
  summarise(mean(bathrooms))
```

```{r}
airdffTrainHawaii%>%
  group_by(high_booking_rate)%>%
  summarise(median(bathrooms))
```

```{r}
#number of beds
airdffTrainHawaii%>%
  group_by(high_booking_rate)%>%
  summarise(median(beds))
```

```{r}
airdffTrainHawaii%>%
  group_by(high_booking_rate)%>%
  summarise(mean(beds))
  
```

```{r}
#Box plot bathroom
plotbathroom <- airdffTrainHawaii %>% 
  ggplot(mapping = aes(x = high_booking_rate, y = bathrooms, fill = factor(high_booking_rate))) + geom_boxplot()

ggplotly(plotbathroom)
```
```{r}
plotbeds <- airdffTrainHawaii %>% 
  ggplot(mapping = aes(x = high_booking_rate, y = beds, fill = factor(high_booking_rate))) + geom_boxplot()

ggplotly(plotbeds)
```

```{r}
#Bedroom
plotbedrooms <- airdffTrainHawaii %>% 
  ggplot(mapping = aes(x = high_booking_rate, y = bedrooms, fill = factor(high_booking_rate))) + geom_boxplot()

ggplotly(plotbedrooms)
```


```{r}
plotprice <- airdffTrainHawaii %>% 
  ggplot(mapping = aes(x = high_booking_rate, y = price, fill = factor(high_booking_rate))) + geom_boxplot()

ggplotly(plotprice)
```


```{r}
plotminnights <- airdffTrainHawaii %>% 
  ggplot(mapping = aes(x = high_booking_rate, y = minimum_nights, fill = factor(high_booking_rate))) + geom_boxplot()

ggplotly(plotminnights)
```

```{r}
plotaccomodates <- airdffTrainHawaii %>% 
  ggplot(mapping = aes(x = high_booking_rate, y = accommodates, fill = factor(high_booking_rate))) + geom_boxplot()

ggplotly(plotaccomodates)
```
```{r}
plotsecurityDeposit <- airdffTrainHawaii %>% 
  ggplot(mapping = aes(x = high_booking_rate, y = security_deposit, fill = factor(high_booking_rate))) + geom_boxplot()

ggplotly(plotsecurityDeposit)
```


```{r}
HawaiiTrain_LM_EX <-
	lm( formula = high_booking_rate ~ price+availability_365+cleaning_fee+host_listings_count+minimum_nights+security_deposit+maximum_nights+extra_people+accommodates+bathrooms+beds+weekly_price+is_location_exact+instant_bookable+bedrooms+market+property_type+cancellation_policy, data = airdffTrainHawaii )

summary(HawaiiTrain_LM_EX)

```



```{r}
HawaiiTrain_LogM_EX <-
	glm(formula = high_booking_rate ~ price+availability_365+cleaning_fee+host_listings_count+minimum_nights+security_deposit+maximum_nights+extra_people+accommodates+bathrooms+beds+weekly_price+is_location_exact+instant_bookable+bedrooms+market+property_type+cancellation_policy, data = airdffTrainHawaii)

summary(HawaiiTrain_LogM_EX)
```

#Predicting model
```{r}
set.seed(555)
trainhbr <- airdffTrainHawaii %>%sample_frac(0.65)
testhbr <- dplyr::setdiff(airdffTrainHawaii,trainhbr)

```

```{r}
trainhbr <-trainhbr %>%dplyr::select(-c('id','access','amenities','description','host_about','host_location','host_neighbourhood','host_verifications','house_rules','interaction','is_business_travel_ready','latitude','longitude','neighborhood_overview','notes','require_guest_phone_verification','require_guest_profile_picture','review_scores_accuracy','review_scores_value','review_scores_rating','space','transit','zipcode','{randomControl}','review_scores_checkin','review_scores_location', 'review_scores_communication','review_scores_cleanliness','availability_90','availability_60','availability_30'))

testhbr <- testhbr %>%dplyr::select(-c('id','access','amenities','description','host_about','host_location','host_neighbourhood','host_verifications','house_rules','interaction','is_business_travel_ready','latitude','longitude','neighborhood_overview','notes','require_guest_phone_verification','require_guest_profile_picture','review_scores_accuracy','review_scores_value','review_scores_rating','space','transit','zipcode','{randomControl}','review_scores_checkin', 'review_scores_location', 'review_scores_communication', 'review_scores_cleanliness','availability_90','availability_60','availability_30'))

```
#Business travel ready holds all false values, review parameter are highly correlated
#

```{r}
trainx <- select(trainhbr,-c('high_booking_rate'))
testx <- select(testhbr,-c('high_booking_rate'))
```


```{r}
dttrain = data.matrix(trainx)
dttest = data.matrix(testx)
```

```{r}
dtrain <- xgb.DMatrix(data = dttrain, label = trainhbr$high_booking_rate)
#dtest <- xgb.DMatrix(data = dttest, label = airdffTestHawaii$high_booking_rate)
```

```{r}
bstair<- xgboost(data=dtrain, max.depth = 14, eta =0.0390,min_child_weight = 2,nthread =8,nrounds = 1200, max_delta_step = 2,colsample_bytree = 0.44, objective = "binary:logistic",verbose = FALSE)
```

```{r}
var_imp <- xgb.importance(model = bstair)
xgb.plot.importance(importance_matrix = var_imp)
```
```{r}
var_imp
```


```{r}
pred <- predict(bstair, dttest)
#pred
```


```{r}
#Confusion Matrix

class_performance <- function(confusion_matrix){
  
  TP <- confusion_matrix[2,2]
  TN <- confusion_matrix[1,1]
  FP <- confusion_matrix[1,2]
  FN <- confusion_matrix[2,1]
  acc <- (TP+TN)/(TP+TN+FP+FN)
  tpr <- TP/(TP+FN)
  tnr <- TN/(TN+FP)
  return(c(acc,tpr,tnr))
}
#Confusion matrix function
confusion_matrix <- function(pred, actuals, cutoff){
  
  classifications <- ifelse(pred>cutoff,1,0)
  
  
  confusion_matrix <- table(actuals,classifications)
}

cm1=confusion_matrix(pred,testhbr$high_booking_rate,0.6)
cm1
metrics1=class_performance(cm1)
metrics1
```


```{r}
library (ROCR);

y <- testhbr$high_booking_rate
predictions <- pred

predx <- prediction(predictions, y);

# Recall-Precision curve             
RP.perf <- performance(predx, "prec", "rec");

plot (RP.perf);

# ROC curve
ROC.perf <- performance(predx, "tpr", "fpr");
plot (ROC.perf);

# ROC area under the curve
auc.tmp <- performance(predx,"auc");
auc <- as.numeric(auc.tmp@y.values)

auc
```


```{r}
#Average Price vs Market

Pricevsmarketplot <- airdffTrainHawaii%>% filter(high_booking_rate ==1) %>%group_by(market)%>%summarize(marketp= mean(price))%>%ggplot+geom_point(mapping = aes(x=market, y = marketp))+theme(axis.text.x = element_text(angle = 90))

ggplotly(Pricevsmarketplot)
```



```{r}
#average price of high_prob vs lower prob in different markets
pricevsmarketvsbookingrate <- airdffTrainHawaii %>% 
  group_by(high_booking_rate,market) %>% 
  summarize(maxFare = max(price), averageFare = mean(price)) %>% 
  ungroup()%>% ggplot+geom_point(mapping=aes(x=market,y = averageFare,color = factor(high_booking_rate)))+ theme(axis.text.x = element_text(angle = 90))

ggplotly(pricevsmarketvsbookingrate)
```





```{r}
#summary(hbrLDA)
```

```{r}
#Number of bedrooms vs market ( color by high booking rate)
bedroomsvsmarketvsbookingrate <- airdffTrainHawaii %>% 
  group_by(high_booking_rate,market) %>% 
  summarize(maxbedroom = max(bedrooms), averagebedroom = mean(bedrooms)) %>% 
  ungroup()%>% ggplot+geom_point(mapping=aes(x=market,y = averagebedroom,color = factor(high_booking_rate)))+ theme(axis.text.x = element_text(angle = 90))

ggplotly(bedroomsvsmarketvsbookingrate)
```

```{r}
bathroomsvsmarketvsbookingrate <- airdffTrainHawaii %>% 
  group_by(high_booking_rate,market) %>% 
  summarize(maxbathroom = max(bathrooms), averagebathroom = mean(bathrooms)) %>% 
  ungroup()%>% ggplot+geom_point(mapping=aes(x=market,y = averagebathroom,color = factor(high_booking_rate)))+ theme(axis.text.x = element_text(angle = 90))

ggplotly(bathroomsvsmarketvsbookingrate)
```

```{r}
#propertyvsmarketvsbookingrate <- airdffTrainHawaii %>% 
  #group_by(property_type,high_booking_rate,market) %>% 
  #ungroup()%>% ggplot+geom_point(mapping=aes(x=market,y = property_type,color = factor(high_booking_rate)))+ theme(axis.text.x = element_text(angle = 90))

#ggplotly(propertyvsmarketvsbookingrate)
```

```{r}
market_occurances <- airdffTrainHawaii %>%
  #filter(high_booking_rate == 1) %>% 
  group_by(market) %>%
  tally()
```



```{r}
market_high <- airdffTrainHawaii %>% filter(high_booking_rate==1)%>%
 group_by(market) %>%
 tally() %>% 
  mutate(pct = 100*n/sum(n))
#proportion_high
#proportion_high <- market_high$n/market_occurances$n
market_high
```

```{r}
```

#Optional

```{r}
# marketvsbookingrate <- market_high %>% 
#   group_by(market) %>% 
#   ungroup()%>% ggplot+geom_point(mapping=aes(x=market,y =pct ,color = factor(high_booking_rate)))+ theme(axis.text.x = element_text(angle = 90))
# ggplotly(marketvsbookingrate)
```

```{r}
occupantsvsmarketvsbookingrate <- airdffTrainHawaii %>% 
  group_by(high_booking_rate,market) %>% 
  summarize(maxaccommodates
 = max(accommodates), averageaccommodates = mean(accommodates)) %>% 
  ungroup()%>% ggplot+geom_point(mapping=aes(x=market,y = averageaccommodates,color = factor(high_booking_rate)))+ theme(axis.text.x = element_text(angle = 90))

ggplotly(occupantsvsmarketvsbookingrate)
```

```{r}
#Avgreview_scores <- airdffTrainHawaii %>% 
  #group_by(market) %>% 
  #mean(as.numeric(review_scores))
#Avgreview_scores
```


```{r}
reviewscoresvsmarketvsbookingrate <- airdffTrainHawaii %>% 
  group_by(high_booking_rate,market) %>% 
  summarize(maxaccommodates
 = max(accommodates), averageaccommodates = mean(accommodates)) %>% 
  ungroup()%>% ggplot+geom_point(mapping=aes(x=market,y = averageaccommodates,color = factor(high_booking_rate)))+ theme(axis.text.x = element_text(angle = 90))

ggplotly(occupantsvsmarketvsbookingrate)
```

```{r}
propertyvsmarketvsbookingrate <- airdffTrainHawaii %>%
  group_by(property_type,high_booking_rate,market) %>% ungroup()%>%
  ggplot+geom_point(mapping=aes(x=property_type,y = market,color = factor(high_booking_rate)))+ theme(axis.text.x = element_text(angle = 90))

ggplotly(propertyvsmarketvsbookingrate)
```

```{r}
MH <- market_high%>% ggplot() + geom_point(mapping=aes(x = market,y = pct, color = "Percentage of high booking rate"))+ theme(axis.text.x = element_text(angle = 90)) +scale_color_manual(values = c("Red"))
ggplotly(MH)
# 
# MHdff <- market_high["market","pct"]
# 
# barplot(MHdff)
```

```{r}
propertyvshighbooking <- airdffTrainHawaii %>%
  filter(high_booking_rate == 1) %>% 
  group_by(market,property_type) %>%
 tally() %>% 
  mutate(proportion = n/sum(n))
 #%>%summarise(max())
propertyvshighbooking %>% arrange(desc(proportion))
```
```{r}
MHvspct <- market_high %>% ggplot(aes(x = reorder(market,-pct),y =pct)) + geom_bar(stat="identity", fill="Blue")+ theme(axis.text.x = element_text(angle = 90))

ggplotly(MHvspct)
```
# Greatest chance of success is if you build in Oahu Island that contains the most popular tourist destinations such as Honolulu and Kailua with one bed to three beds and One bathroom. Largely individual families? Greatest odds of success is if the price is between $99 and 185 and the larger number of property's rent is $131. where as anything above $185 has greater odds of faiure. Individual/independent houses allow for the highest odds of success.Hotels are bad and the odds of success drastically improve. Coming to cancellation policy moderation is key. You will get lose out if you are super strict. Private rooms are the best. One is ideal.Shared room is a bad idea.
---
References:

https://www.hawaiitourismauthority.org/news/news-releases/2020/hawai-i-visitor-statistics-released-for-2019/


---
